Energy Regulation for Biologically-Inspired Robotics

### 2021-09-20 latex/nserc/proposal.tex
Final version of proposal, ready to submit.

%---------- Main Content ----------%
A robotic monkey swings through jungle trees, capturing valuable
wildlife data without disturbing the local environment. 
In a nearby city, a robotic police dog runs through the streets, weaving through
pedestrians' legs to catch a thief.
It passes a traveling circus group, where robot gymnasts perform elaborate
routines in front of an awestruck audience.
This world sounds like science fiction, but it is truly within sight;
the research we propose below will enable roboticists to accurately recreate
human and animal behaviour in their robots.
This world we imagined can become a present-day reality.

@@

Before can explain how these humanoid and animal-like robots will work, we
must first understand how humans and animals move. 
Take the example of a human gymnast who  wants to do backflips around a
horizontal bar. 
The gymnast starts by swinging their legs based on their current speed and
position in a technique called a ``giant" \cite{usagym_giant}. 
This allows them to generate enough momentum to rotate around the bar.

@@

Using VNHCs for \textit{energy injection} is beneficial because it allows robots to
safely and reliably increase their momentum.
Likewise, designing VNHCs for \textit{energy dissipation} allows robots to
safely and realistically slow down.
In this PhD, I propose to further study the energy regulation properties of VNHCs.
First, we will find mathematical conditions under which VNHCs are guaranteed to
inject or dissipate energy in fixed-base robots.
Then we will design a means of transitioning between two different VNHCs,
enabling us to regulate a robot's energy in a provably safe manner.
We will experimentally verify the results of this theory on the acrobot by
designing a gymnastics routine which is performed solely by transitioning
between different virtual constraints.
Finally, we will extend the theory to mobile animal-like robots,
and we will build a robotic monkey which uses VNHCs to swing on monkey bars just
like a real monkey would swing through trees.

@@

\newpage
%---------- Bibliography ----------%
\printbibliography
\end{document}

>>>>

%---------- Main Content ----------%
A robotic monkey swings through jungle trees, capturing valuable
wildlife data without disturbing the local environment. 
In a nearby city, a robotic police dog runs through the streets, weaving through
pedestrians' legs to catch a thief.
It passes a traveling circus group, where robot gymnasts perform elaborate
routines in front of an awestruck audience.
This world sounds like science fiction, but it is truly within sight:
the research we propose below will enable roboticists to accurately recreate
human and animal behaviour in their robots.
This world we imagined can become a present-day reality.

@@

Before we can explain how these humanoid and animal-like robots will work, we
must first understand how humans and animals move. 
Take the example of a human gymnast who  wants to do backflips around a
horizontal bar. 
The gymnast starts by swinging their legs in a technique called a ``giant"
\cite{usagym_giant}, during which they move their legs based on their current
position and velocity \cite{pendulum_length_giant_gymnastics}. 
This allows them to generate enough momentum to rotate around the bar.

@@

Using VNHCs for \textit{energy injection} is beneficial because it allows robots to
safely and reliably increase their momentum.
Likewise, designing VNHCs for \textit{energy dissipation} allows robots to
safely and realistically slow down.
In this PhD, I propose to further study the energy regulation properties of VNHCs.
First, we will find mathematical conditions under which VNHCs are guaranteed to
inject or dissipate energy in fixed-base robots.
Then we will design a means of transitioning between two different VNHCs,
enabling us to regulate a robot's energy in a provably safe manner.
We will experimentally verify the results of this theory on the acrobot by
designing a gymnastics routine which is performed solely by transitioning
between different virtual constraints.
Finally, we will extend the theory to mobile animal-like robots,
and we will build a robotic monkey which uses VNHCs to swing on monkey bars just
like a real monkey would swing through jungle trees.

@@

\newpage
%---------- Bibliography ----------%
\pagenumbering{arabic}
\printbibliography
\end{document}
